The merger history of primordial-black-hole binaries inferred from GWTC-3

### 2022-09-26 latex/paper.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\title{The merger history of primordial-black-hole binaries implied by GWTC-3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\author{Zu-Cheng~Chen}
%\email{zucheng.chen@bnu.edu.cn}
%\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
%\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\author{You~Wu}
%\email{Corresponding author: youwuphy@gmail.com}
%\affiliation{College of Mathematics and Physics, Hunan University of Arts and Science, Changde, 415000, China}

@@

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
in \Fig{posterior-log}.
\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{posterior-log.pdf}
	\caption{\label{posterior-log}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{posterior-power.pdf}
	\caption{\label{posterior-power}
		The marginalized one- and two-dimensional posterior distributions for 
    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\title{The merger history of primordial-black-hole binaries inferred from GWTC-3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Zu-Cheng~Chen}
\email{zucheng.chen@bnu.edu.cn}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Zhi-Qiang~You}
\email{zhiqiang.you@bnu.edu.cn}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{You~Wu}
\email{youwuphy@gmail.com}
\affiliation{College of Mathematics and Physics, Hunan University of Arts and Science, Changde, 415000, China}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Lang~Liu}
\email{Corresponding author: liulang@bnu.edu.cn}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}

@@

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
in \Fig{posterior-log}.
\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{post-log.pdf}
	\caption{\label{posterior-log}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{post-power.pdf}
	\caption{\label{posterior-power}
		The marginalized one- and two-dimensional posterior distributions for 
    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}
